Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-13 Code/Manuscript_O2.Rmd
edit ocean protein captions

ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as from Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

ProchloroElectronTrans_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as from FtsH1, FtsH2, FtsH3 or Ribosome).",
                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

>>>>

ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as from Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "Horizontal grey lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
                       "Vertical grey lines indicate O~2~ (µM) used for  later culture growth.",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

ProchloroElectronTrans_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as from FtsH1, FtsH2, FtsH3 or Ribosome).",
                       "Horizontal grey lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
                       "Vertical grey lines indicate O~2~ (µM) used for  later culture growth.",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")
